### 2009-04-11 docs/runtime_parameters/runtime_parameters.tex
made use_eos_coulomb=.true. by default in probin
made do_initial_projection a logical instead of int.

modified do_initial_projection in all inputs files
some formatting

\verb=  base_cutoff_density =  & Refer to Section \ref{Sec:Base Cutoff Density}  &  3.e6 \\
\verb=  bcx_hi =  & $+x$ boundary condition (valid values are listed in {\tt  boxlib/bc.f90})  &  SLIP\_WALL \\

@@

\verb=  beta_type =  & what type of coefficient to use inside the velocity divergence constraint.  
                           {\tt beta\_type} = 1 uses $\beta_0$; {\tt beta\_type} = 2 uses $\rho_0$ (anelastic);

@@

\verb=  cflfac =  & CFL factor to use in the computation of the advection timestep constraint  &  0.5 \\

@@

\verb=  co_latitude =  & latitude, in radians, for problems with rotation where the domain is only a subset
                             of a full star.  &  ZERO \\

@@

\verb=  do_eos_h_above_cutoff =  & After the advective enthalpy update, recompute the enthalpy if we are 
                                         below the base cutoff density.   &  .true. \\
\verb=  do_initial_projection =  & Do the initial projection.  & 1 \\

@@

\verb=  dpdt_factor =  & factor in front of the volume discrepancy term (0.0 = off)  &  0.0d0 \\
\verb=  drdxfac =  & ratio of radial base state zones to Cartesian full state zones for spherical geometry  &  1 \\
\verb=  enthalpy_pred_type =  & predict\_rhohprime = 1; predict\_h = 2; predict\_T\_then\_rhohprime = 3;
                                      predict\_T\_then\_h = 4; predict\_hprime = 5; predict\_Tprime\_then\_h = 6;
                                    &  predict\_rhohprime \\
\verb=  evolve_base_state =  & turn on (.true.) or off (.false.) basestate evolution  &  .true. \\
\verb=  fixed_dt =  & Fix the time step.  If -1.0, then use the standard time step.  &  -1.0d0 \\
\verb=  grav_const =  & the gravitational acceleration (cm~s$^{-2}$) for plane-parallel geometry  &  -1.5d10 \\

@@

\verb=  hg_dense_stencil =  & In hgproject, 
                                   In 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).
                                   In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.). &  .true. \\

@@

\verb=  init_shrink =  & the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the 
                             various timestep estimators   &  1.0 \\
\verb=  interp_type_radial_bin_to_cart =  & The interpolation for filling a full multifab from a 1D 
                                                     bin-centered array.  1 = piecewise constant; 

@@

\verb=  lUsingNFiles =  & If .true., use nOutFiles processors to write checkpoint and plotfiles.  
                              Fortran has the unfortunate feature of each processor only being able to write out 

@@

\verb=  max_dt_growth =  & The maximum scale factor that the time step is allowed to grow by per time step.  
                              &  1.1D0 \\
\verb=  max_grid_size =  & The largest grid size that will be created using make\_new\_grids.  &  64 \\

@@

\verb=  mg_verbose =  & Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\

@@

\verb=  min_width =  & The minimum size on a side  for a grid created using make\_new\_grids.  &  16 \\

@@

\verb=  nOutFiles =  & If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  
                           Fortran has the unfortunate feature of each processor only being able to write out 
                           1-2GB each without crashing.  & 64 \\
\verb=  perturb_model =  & Turn on a perturbation in the initial data.  Problem specific.  &  .false. \\

>>>>

\verb=  base_cutoff_density =  & Refer to Section \ref{Sec:Base Cutoff Density}  
                                     &  3.e6 \\
\verb=  bcx_hi =  & $+x$ boundary condition (valid values are listed in 
                       {\tt  boxlib/bc.f90})  &  SLIP\_WALL \\

@@

\verb=  beta_type =  & what type of coefficient to use inside the velocity divergence 
                           constraint.  {\tt beta\_type} = 1 uses $\beta_0$; 
                           {\tt beta\_type} = 2 uses $\rho_0$ (anelastic);

@@

\verb=  cflfac =  & CFL factor to use in the computation of the advection timestep 
                       constraint  &  0.5 \\

@@

\verb=  co_latitude =  & latitude, in radians, for problems with rotation where the 
                             domain is only a subset of a full star.  &  ZERO \\

@@

\verb=  do_eos_h_above_cutoff =  & After the advective enthalpy update, recompute 
                                          the enthalpy if we are below the base cutoff 
                                          density.   &  .true. \\
\verb=  do_initial_projection =  & Do the initial projection.  & .true. \\

@@

\verb=  dpdt_factor =  & factor in front of the volume discrepancy term (0.0 = off)  
                           &  0.0d0 \\
\verb=  drdxfac =  & ratio of radial base state zones to Cartesian full state zones for 
                        spherical geometry  &  1 \\
\verb=  enthalpy_pred_type =  & predict\_rhohprime = 1; predict\_h = 2; 
                                      predict\_T\_then\_rhohprime = 3;
                                      predict\_T\_then\_h = 4; predict\_hprime = 5; 
                                      predict\_Tprime\_then\_h = 6;  &  predict\_rhohprime \\
\verb=  evolve_base_state =  & turn on (.true.) or off (.false.) basestate evolution  
                                   &  .true. \\
\verb=  fixed_dt =  & Fix the time step.  If -1.0, then use the standard time step.  
                        &  -1.0d0 \\
\verb=  grav_const =  & the gravitational acceleration (cm~s$^{-2}$) for plane-parallel 
                            geometry  &  -1.5d10 \\

@@

\verb=  hg_dense_stencil =  & In hgproject, in 2D, use a 9 point Laplacian (.true.) 
                                    or 5-point Laplacian (.false.).  In 3D, use a 27 point 
                                    Laplacian (.true.) or 7-point Laplacian (.false.). 
                                  &  .true. \\

@@

\verb=  init_shrink =  & the multiplicative factor ($\le 1$) to reduce the initial 
                             timestep as computed by the various timestep estimators   
                            &  1.0 \\
\verb=  interp_type_radial_bin_to_cart =  & The interpolation for filling a full 
                                                     multifab from a 1D bin-centered array.  
                                                     1 = piecewise constant; 

@@

\verb=  lUsingNFiles =  & If .true., use nOutFiles processors to write checkpoint and 
                               plotfiles.  Fortran has the unfortunate feature of each 
                               processor only being able to write out 

@@

\verb=  max_dt_growth =  & The maximum scale factor that the time step is allowed to 
                                grow by per time step.  &  1.1D0 \\
\verb=  max_grid_size =  & The largest grid size that will be created using 
                                make\_new\_grids.  &  64 \\

@@

\verb=  mg_verbose =  & Verbsoity of the multigrid solver, but not the bottom solver.  
                          &  0 \\

@@

\verb=  min_width =  & The minimum size on a side  for a grid created using 
                           make\_new\_grids.  &  16 \\

@@

\verb=  nOutFiles =  & If lUsingNFiles = .true., use this many processors to write 
                           checkpoint and plotfiles.  Fortran has the unfortunate feature 
                           of each processor only being able to write out 1-2GB each 
                           without crashing.  & 64 \\
\verb=  perturb_model =  & Turn on a perturbation in the initial data.  
                                Problem specific.  &  .false. \\
